---
title: "Data Visualization"
author: "eusha54"
geometry: margin=1in
format:
  pdf:
    code-overflow: wrap
---

1.  Read and view the first 5 rows of the Data

```{r}
library(datasets)

data(mtcars)
  # loading data
head(mtcars, 5)
  # first 5 rows of data
```

2.  type the following to get info about the a variable

```{r}
# ?mtcars
```

\newpage

3.  use the following code to create a scatterplot of two variables disp and mpg

```{r}
library(ggplot2)
  # loading ggplot package

ggplot(aes(x=disp, y=mpg), data=mtcars) + geom_point()
```

\newpage

4.  add title and labels to the last plot

```{r}
#| code-overflow: wrap
ggplot(aes(x=disp, y=mpg), data=mtcars) + geom_point() + ggtitle("displacement vs miles per gallon") + labs(x="Displacement", y="Miles per Gallon")
```

\newpage

5.  Use the following to create a boxplot of the the distribution of mpg for the individual Engine types vs Engine (0 = V-shaped, 1 = straight) To do this you have to make vs a string or factor.

```{r}
#make vs a factor
mtcars$vs <- as.factor(mtcars$vs)

#create boxplot of the distribution for v-shaped and straight Engine

ggplot(aes(x=vs, y=mpg), data = mtcars) + geom_boxplot()
```

\newpage

6.  add color to boxplot

```{r}
ggplot(aes(x=vs, y=mpg, fill=vs), data=mtcars) + geom_boxplot(alpha=0.3) + theme(legend.position = "none")
```

7.  histogram of single variable.

```{r}
ggplot(aes(x=wt), data=mtcars) + geom_histogram(binwidth = 0.5)
```
